---
title: "pA1__Template"
author: "Nimisha"
date: "21/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reproducible research - course proj 1
```{r}
setwd("C:/Users/NIMISHA/Documents/Reproducible research")
data1 <- read.csv("activity.csv",sep = ",")
summary(data1)
dim(data1)
str(data1)

library(ggplot2)
library(dplyr)

```


## Calculating number of steps each day.
```{r}
steps_each_day<-aggregate(x=list(steps=data1$steps),by=list(date=data1$date),sum,na.rm=TRUE)
head(steps_each_day)
```
### 3. Explaining the variation of the number of steps taken by the person each day
```{r}
hist(steps_each_day$steps,col="red",main = "Variation in the Number of steps",xlab ="Number of Steps Each Day" )
```
#### 4. Mean and median number of steps taken each day
```{r}
 mean_steps<-mean(steps_each_day$steps,na.rm=TRUE)
 median_steps<-median(steps_each_day$steps,na.rm=TRUE)

```
##### 5. Calculating average in each time interval across all days and making a line plot.
```{r}
avg_steps_each_interval<- aggregate(x=list(steps=data1$steps),by=list(interval=data1$interval),mean,na.rm=TRUE)
max_<-which.max(avg_steps_each_interval$steps)
max_steps<-avg_steps_each_interval[max_,'steps']
ggplot(data = avg_steps_each_interval,aes(x=interval,y=steps))+geom_line(col="blue")+labs(title = "Average Number of Steps in Each Interval")

```
###### Finding index of all those entries which are filled as NA in the dataset
```{r}
filled_data<-data1
na_index<-which(is.na(data1))
```
7.	Imputing all those values in the dataset which are not available.
```{r}
for(i in na_index){
        interval_of_data<-filled_data[i,'interval']
        filled_data[i,'steps']<-avg_steps_each_interval[avg_steps_each_interval$interval==interval_of_data,'steps']
        
}
```
##### Calculating number of steps taken each day and other basic statistics for complete data.
```{r}
num_steps<-aggregate(x=list(steps=filled_data$steps),by=list(date=filled_data$date),sum)
mean_steps<-mean(num_steps$steps)
median_steps<-median(num_steps$steps)
ggplot(data=num_steps,aes(steps))+geom_histogram(col="red",bins = 8)+labs(title = "Number of Steps Taken Each Day")+xlab(label = c("Steps"))
```
#### Making new column and filling the data that whether the day was a weekday or a weekend and plotting the acivity on weekend and weekday.
```{r}
filled_data$weekday<-weekdays(as.Date(filled_data$date))

filled_data$weekday<-ifelse(filled_data$weekday=="Saturday"|filled_data$weekday=="Sunday","Weekend","Weekday")
levels(filled_data$weekday)<-c("Weekend","Weekday")

data_for_plot<-aggregate(x=list(steps=filled_data$steps),by=list(interval=filled_data$interval,weekday=filled_data$weekday),mean)

g<-ggplot(data = data_for_plot,aes(x=interval,y=steps))+geom_line(col="blue")
g+facet_grid(weekday~.)+labs(title = "Activity on different type of days")+xlab(label = "5 minute interval")
```
